### 2014-11-12 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Minor edits to flow path description in abstract; fix LaTeX warnings

% PDF metadata
\hypersetup{
  pdftitle={Simulation of a Fire in a Hillside Residential Structure - San Francisco, CA},
  pdfauthor={Overholt, Kristopher J., Weinschenk, Craig G., and Madrzykowski, Daniel},
  pdfsubject={The Fire Dynamics Simulator (FDS) fire model, which is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on June 2, 2011, within a multi-level, single-family residential structure in San Francisco, CA, that resulted in the death of two firefighters. The inputs for the FDS simulation are documented in this report and are based on the fire scenario, including the building geometry, interior furnishings, and ventilation conditions. The fire started in the basement and resulted in ventilation limited (fuel rich) fire conditions in the basement area. The fire originated in the basement, and the interior stairwell acted as a chimney for hot gases in the basement to flow towards regions of lower pressure via the interior stairwell towards the front of the structure. After the rear basement windows began to fail, the combustion gases at elevated temperature and pressure in the basement flowed upwards towards lower pressure regions via the stairwell. The temperature of the gases in the interior stairwell was estimated to be in excess of 700~$^{\circ}$C (1300~$^{\circ}$F). Two firefighters were located in the flow path between the basement and the doors on the front side of the structure, were exposed to these elevated temperatures, and later died as a result of their injuries.},
  pdfkeywords={flow path; fire dynamics; LODD; fire modeling; FDS simulation}
}

@@

The Fire Dynamics Simulator (FDS) fire model, which is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on June 2, 2011, within a multi-level, single-family residential structure in San Francisco, CA, that resulted in the death of two firefighters. The inputs for the FDS simulation are documented in this report and are based on the fire scenario, including the building geometry, interior furnishings, and ventilation conditions. The fire started in the basement and resulted in ventilation limited (fuel rich) fire conditions in the basement area.

The fire originated in the basement, and the interior stairwell acted as a chimney for hot gases in the basement to flow towards regions of lower pressure via the interior stairwell towards the front of the structure. After the rear basement windows began to fail, the combustion gases at elevated temperature and pressure in the basement flowed upwards towards lower pressure regions via the stairwell. The temperature of the gases in the interior stairwell was estimated to be in excess of 700~$^{\circ}$C (1300~$^{\circ}$F). Two firefighters were located in the flow path between the basement and the doors on the front side of the structure, were exposed to these elevated temperatures, and later died as a result of their injuries.

@@

The fire originated in the basement, and the interior stairwell acted as a chimney for hot gases in the basement to flow towards regions of lower pressure via the interior stairwell towards the front of the structure. After the rear basement windows failed, a flow path was established between the basement living room area and the doors located on the front side of the structure (the front door and the garage door). The rear basement window failures resulted in a rapid change in the conditions within the flow path. After the rear basement windows began to fail, the combustion gases at elevated temperature and pressure in the basement flowed upwards towards lower pressure regions via the stairwell. In the interior stairwell, the flow velocities were approximately 9~m/s (20~mph) and the temperature of the gases was estimated to be in excess of 700~$^{\circ}$C (1300~$^{\circ}$F), which exceeds the Class~III exposure temperature of 260~$^{\circ}$C (500~$^{\circ}$F).

>>>>

% PDF metadata
\hypersetup{
  pdftitle={Simulation of a Fire in a Hillside Residential Structure - San Francisco, CA},
  pdfauthor={Overholt, Kristopher J., Weinschenk, Craig G., and Madrzykowski, Daniel},
  pdfsubject={The Fire Dynamics Simulator (FDS) fire model, which is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on June 2, 2011, within a multi-level, single-family residential structure in San Francisco, CA, that resulted in the death of two firefighters. The inputs for the FDS simulation are documented in this report and are based on the fire scenario, including the building geometry, interior furnishings, and ventilation conditions. The fire started in the basement and resulted in ventilation limited (fuel rich) fire conditions in the basement area. After the rear basement windows began to fail, the interior stairwell acted as a chimney for hot gases in the basement to flow towards regions of lower pressure and vent openings located on the front side of the structure. The temperature of the gases in the interior stairwell was estimated to be in excess of 700~C (1300~F). Two firefighters were located in the flow path between the basement and the doors on the front side of the structure, were exposed to these elevated temperatures, and later died as a result of their injuries.},
  pdfkeywords={flow path; fire dynamics; LODD; fire modeling; FDS simulation}
}

@@

The Fire Dynamics Simulator (FDS) fire model, which is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on June 2, 2011, within a multi-level, single-family residential structure in San Francisco, CA, that resulted in the death of two firefighters. The inputs for the FDS simulation are documented in this report and are based on the fire scenario, including the building geometry, interior furnishings, and ventilation conditions. The fire started in the basement and resulted in ventilation limited (fuel rich) fire conditions in the basement area. After the rear basement windows began to fail, the interior stairwell acted as a chimney for hot gases in the basement to flow towards regions of lower pressure and vent openings located on the front side of the structure. The temperature of the gases in the interior stairwell was estimated to be in excess of 700~$^{\circ}$C (1300~$^{\circ}$F). Two firefighters were located in the flow path between the basement and the doors on the front side of the structure, were exposed to these elevated temperatures, and later died as a result of their injuries.

@@

The fire originated in the basement, and the interior stairwell acted as a chimney for hot gases in the basement to flow towards regions of lower pressure and vent openings located on the front side of the structure. After the rear basement windows failed, a flow path was established between the basement living room area and the doors located on the front side of the structure (the front door and the garage door). The rear basement window failures resulted in a rapid change in the conditions within the flow path. In the interior stairwell, the flow velocities were approximately 9~m/s (20~mph) and the temperature of the gases was estimated to be in excess of 700~$^{\circ}$C (1300~$^{\circ}$F), which exceeds the Class~III exposure temperature of 260~$^{\circ}$C (500~$^{\circ}$F).
